Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2019-03-15 paper/ms.tex
Couple o' quick things from discussing the manuscript at group meeting.

Supernovae are classified observationally
by their light curves and spectra~\citep{minkowski41,bertola64,porterfilippenko87,
wheelerharkness1990conf,Fili97}, with the type Ia designation following from
the absence of H in the spectrum and the presence of a specific Si
line~\citep{filippenko:optical,hillebrandt.niemeyer:type}. These events
have been associated with C burning under degenerate conditions
for some time~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis},
but discerning the setting(s) of these events is proving difficult
and remains the subject of active research. At present there are three
widely-accepted scenarios: the {\em single degenerate} scenario,
the {\em double detonation} or {\em sub-Chandrasekhar} scenario, and
the {\em white dwarf merger} or {\em double degenerate} scenario.
We briefly describe these in the subsection that follows.
Also see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013,roepkesim2018}
for additional discussion.

@@

Figure \ref{fig:masshighdens} compares the final yield of IGE elements
for the C-O and C-O-Ne simulation suites with the amount of expansion of the
WD during the deflagration phase. The amount of expansion is
characterized by the mass above $2 \times 10^7~\grampercc$ at the
time of the DDT, with more high-density mass
indicating less expansion during deflagration. The averages of both
the C-O and C-O-Ne suites along both axes are indicated by the shaded
regions with $\pm1\sigma$ widths.

>>>>

Supernovae are classified observationally
by their light curves and spectra~\citep{minkowski41,bertola64,porterfilippenko87,
wheelerharkness1990conf,Fili97}, with the type Ia designation following from
the absence of H in the spectrum and the presence of a specific Si
line~\citep{filippenko:optical,hillebrandt.niemeyer:type}. These events
have been associated with C burning under degenerate conditions
for some time~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis},
but discerning the setting(s) of these events is proving difficult
and remains the subject of active research. At present there are three
widely-accepted scenarios: the {\em single degenerate} scenario,
the {\em double detonation} or {\em sub-Chandrasekhar} scenario, and
the {\em white dwarf merger} scenario.
We briefly describe these in the subsection that follows.
Also see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013,roepkesim2018}
for additional discussion.

@@

Figure \ref{fig:masshighdens} compares the final yield of IGEs
for the C-O and C-O-Ne simulation suites with the amount of expansion of the
WD during the deflagration phase. The amount of expansion is
characterized by the mass above $2 \times 10^7~\grampercc$ at the
time of the DDT, with more high-density mass
indicating less expansion during deflagration. The averages of both
the C-O and C-O-Ne suites along both axes are indicated by the shaded
regions with $\pm1\sigma$ widths.
